---
title: "EPID674 Epidemiologic Data Analysis using R"
subtitle: "Not Graded Optional Homework 7A"
author: "Insert Your Name Here"
date: "Last compiled on `r format(Sys.Date(), '%B %d, %Y')`"
output:
  word_document: default
---

# Note, this is an optional, ungraded assignment
```{r setup}
knitr::opts_chunk$set(echo = TRUE)

library(foreign)
library(epiDisplay)
library(stats)
library(Hmisc)
library(gmodels)
library(here)

```

# Use the NHANES3 dataset (from class) to test the following:

# Covariates: age, factor(sex), factor(race), factor(educ), factor(smk), factor(alc)


# Problem 1
## Examine the association between blood lead and cardiovascular mortality (d_cvd) over time (pmon_mec). Use the covariates (confounders) considered above. Check which covariates violate the proportional hazard assumption.
```{r problem 1}
#Insert code for problem 1 here
```
# Interpret results for problem 1 here

# Problem 2
## Compute hazard ratio (HR) (95% CI) per for a 1-SD increase in blood lead using the covariates above.
```{r problem 2}
#Insert code for problem 2 here
```
# Include residuals histogram here
# Interpret results for problem 2 here

# Problem 3
# Compare the lowest vs. the highest tertiles of blood lead using the covariates above. Compute HR and 95% CI.
```{r problem 3}
#Insert code for problem 3 here
```
# Interpret results for problem 3 here


